---
title: "QMM_ASSIGNMENT DEA"
author: "Yeswanth Siripurapu"
date: "2023-11-06"
output:
  pdf_document: default
  html_document: default
---

# The code will read the file energy.csv and store all of the data in a 
#DataFrame called Energy.
#The input code is too short to provide a detailed and accurate answer. To gain deeper insight, try again using a longer piece of code.

```{r}
Energy <- read.csv("D:/energy.csv")
```

#The code is a benchmarking code that will be run in the R environment.
#The input code is too short to provide a detailed and accurate answer. To gain deeper insight, try again using a longer piece of code.

```{r}
library(Benchmarking)

```

#The code is a function that takes in two vectors and returns the correlation 
#between them.
#The first vector is the size of the power grid, which is stored as D.C..Size, 
#and the second vector is how many times it has shut down over time, which is stored as Shut.Downs.
#The code starts by creating an empty list called e with three elements: x, y, 
#and RTS="crs".
#This means that x will be used to store data about the size of power grids 
#(D.C.), y will be used to store data about how often they have shut down
#(Shutdowns), and RTS=3 tells us what type of correlation we are looking for:
#Pearson's r-squared value 3 or Spearman's rank order correlation coefficient 3
#The code is designed to create a time series plot of energy consumption and queue time.

```{r}
x1=Energy$D.C..Size
x2=Energy$Shut.Downs
y1=Energy$Computing.Time..h.
x=matrix(c(x1,x2),ncol=2)
y2=Energy$MWh.Consumed
y3=Energy$Queue.Time..ms.
y=matrix(c(y1,y2,y3),ncol=3)
colnames(y)= c("Computing.Time..h.","MWh.Consumed","Queue.Time..ms.")
colnames(x)=c("D.C..Size","Shut.Downs")
x
y

e=dea(x,y,RTS="crs")
e
peers(e)

lambda(e)

#dea.plot.transform(y[,1],y[,2],RTS=3)
```